%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.5in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}


\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Vlad Papchenko}{Last update on \today}
\\\\\\
{\bf Senior Backend Developer/Software Architect}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

\noindent\href{mailto:v.e.papchenko.at.gmail.dot.com}{v.e.papchenko\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}972 53-543-9214\sbull
%{\newnums cies010} \emph{(Skype)}\sbull
\href{https://www.linkedin.com/in/vladimir-papchenko}{www.linkedin.com/in/vladimir-papchenko}\sbull
\href{https://github.com/gecec}{github.com/gecec}
\\
% Mathenesserplein 84\sbull
% 3022\thinspace {\large \sc ld}\sbull
% Haifa\sbull
Israel

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\inlineheadsection
\noindent
{}
A motivated software developer with strong problem-solving skills and great attention to detail, seeking to build on a robust knowledge of software development principles. I know how to make real-life data processing efficient and stable, choosing the best algorithms for optimal performance. I'm a strong advocate for reliable, high-quality code. Ready for new challenges in a professional environment where I can apply my best efforts with full dedication and enthusiasm to accomplish given tasks.

\spacedhrule{0.2em}{-0.3em}
\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Software design and implementation. Solid knowledge of algorithms, Object Oriented Programming, Java, design patterns, Spring Framework, Spring Boot, Spring Cloud, Docker, multithreading, AWS, Cloud Foundry, RabbitMQ, REST, SQL, JUnit, Mockito, Tomcat, JBoss/Wildfly, Git, Maven, GitHub actions, microservice architecture. I have experience with many data storage technologies: PostgreSQL, Vertica, Oracle, MS SQL Server, Elastic, Greenplum. Familiar with other languages such as Go and Python. I have base knowledge of frontend technologies: HTML, CSS, Javascript, ReactJS. Linux advanced user.}

\vspace{0.3em}
\inlineheadsection
  {Natural languages:}
  {English \emph{(fluent)}, Hebrew \emph{(upper intermediate)}, Russian \emph{(native)}}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.philips.co.il/}{Philips Medical}}
  {\textsc{Israel}} {%
  \headedsubsection
    {Lead Developer/ Software Architect}
    {2021 -- now}
    {\bodytext{Working as a Lead Developer and Software Architect in a backend platform team. Hands-on experience in implementing the most complex features and critical system components. Designing system architecture and features, mentoring developers.}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.cognyte.com/}{Cognyte (former Verint Systems)}}
  {\textsc{Israel}} {%
  \headedsubsection
    {Senior Software Developer}
    {2019 -- 2021}
    {\bodytext{I worked in a backend development team, implementing new features and maintaining existing ones while migrating a large monolithic system to a microservice architecture using the Spring Boot and Spring Cloud technology stack. Participated in system design tasks, conducted code reviews, and mentored junior developers.}}
}

%\headedsection  % sets the header for the section and includes any subsections
%  {\href{}{Freelance}}
%  {\textsc{}} {%
%  \headedsubsection
%    {Software Developer}
%    {2018 -- 2019}
%    {\bodytext{I worked as a freelancer for a small project that helped to manage and monitor self-driving trucks. I've developed backend and frontend parts of the system. Backend was built using Java, Spring Boot, Docker, MongoDB, RabbitMQ, frontend - using ReactJS and LeafletJS. I also took part in system design and architecture development.}}
%  }

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.rtlabs.ru}{RTLabs}}
  {\textsc{Samara, Russia}} {%
  \headedsubsection
    {Java Developer}
    {2017 -- 2019}
    {\bodytext{RTLabs is a big development company that builds large scalable systems for Russian electronic governmnent. I was developing projects helping to design protocols and interfaces for messaging through a huge information bus. Firstly, I rewrote one of the projects from Java 7 to Java 8 and Spring Boot. Then I was a leading backend developer at the next project, took part in building of system architecture, implemented backend (Java, PostgreSQL) and frontend parts (JSF). I also participated in other RTLabs projects in Java mostly making backend parts and small pieces of frontend.}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{http://inform.gazprom.ru/}{Gazprom Inform}}
  {\textsc{Samara, Russia}} {%
  \headedsubsection
    {Senior Software Engineer}
    {2013 -- 2017}
    {\bodytext{Gazprom Inform is an IT-company providing solutions based on SAP. I was an ABAP programmer there. I developed accounting, financial and real-estate modules of SAP project for a big Gazprom branch. I participated in integration of our system with a central one using SAP XI-PI platform. I developed sub-modules for tax calculation and reporting to Russian Tax Ministry. }}
}

\headedsection
  {\href{http://www.rzd.ru/}{RZD}}
  {\textsc{Samara, Russia}} {%

  \headedsubsection
    {Software Developer}
    {2008 -- 2012}
    {\bodytext{I worked at a huge IT-department of Russian Railway company (RZD). I was a software developer in Java(Spring, Tomcat), Delphi, PHP, Javascript. I used Oracle and MS SQL Server databases. Also I developed infrastructure tools in Perl, Python and Bash.}}
}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.samgups.ru}{Samara State Railway University}}
  {\textsc{Samara, Russia}} {%
  \headedsubsection
    {MSc in Computer Science}
    {2004 -- 2009}
    {\bodytext{Got knowledge of computer science, software design and development, information theory, cybersecurity and networks. Took part in regional programming contests.}}
}

% \headedsection
%   {\href{http://www.tudelft.nl/en}{Samara State Railway University}}
%   {\textsc{Samara, Russia}} {%
%   \headedsubsection
%     {Studied for Ph.D.}
%     {2009 -- 2012}
%     {\bodytext{Mathematical modeling, numerical methods and software complexes.}}
% }

% \headedsection
%   {\href{http://www.libanonlyceum.nl}{Samara State Railway University}}
%   {\textsc{Samara, Russia}} {%
%   \headedsubsection
%     {Interpreter in professional area (IT, English) \textnormal{~(secondary education)}}
%     {2005 -- 2008} {}
% }

\spacedhrule{0.5em}{-0.4em}



% \roottitle{Side projects}
%
% \inlineheadsection
%   {Telegram bot for learning Hebrew.}
%   {Built with Java, Spring Boot and Telegram Bots API.}


\end{document}

＀
